Difference Scores: Paired Samples T-test

### 2024-03-06 examples/_1a_Examples_DifferenceScores_PairedTtests.qmd
updates

```{r read-data}
#| echo: TRUE
#| messages: FALSE
#| warning: FALSE
#| output: FALSE
#| cache: FALSE

@@

@@

```{r}
# Install and load the googledrive package
if (!requireNamespace("googledrive", quietly = TRUE)) install.packages("googledrive")
library(googledrive)

@@

>>>>

<!-- ```{r read-data}
#| echo: TRUE
#| messages: FALSE
#| warning: FALSE
#| output: FALSE
#| cache: FALSE

@@

```
::: -->

@@

<!-- ```{r}
# Install and load the googledrive package
if (!requireNamespace("googledrive", quietly = TRUE)) install.packages("googledrive")
library(googledrive)

@@

``` -->

```{r}
# Set the URL for the CSV file
file_url <- "https://drive.google.com/file/d/1_gnaEx0wJ28tT0CD_B6mPFwngdfSb6Dr/view?usp=drive_link"

# Set the destination filename
dest_file <- "my_data.rds"

# Download the file
download.file(file_url, destfile = dest_file, mode = "wb")

# Read the CSV file into R
my_data <- readRDS(dest_file)

# Display the first few rows of the data
head(my_data)
```
